Unprepared colonoscopy identifies microbiota specific to the proximal and distal

### 2017-07-21 submission/manuscript.Rmd
fixed the bug

---
title: Unprepared colonoscopy identifies microbiota specific to the proximal and distal human colon
csl: mbio.csl
fontsize: 11pt
output:
  pdf_document:
    includes: null
    keep_tex: yes
  html_document: default
  word_document: default
geometry: margin=1.0in
bibliography: references.bib
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
---
\vspace{35mm}

>>>>

---
title: Unprepared colonoscopy identifies microbiota specific to the proximal and distal
  human colon
csl: mbio.csl
fontsize: 11pt
output:
  pdf_document:
    includes: null
    keep_tex: yes
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
geometry: margin=1.0in
bibliography: references.bib
---
\vspace{35mm}
